cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Added application with more close clusters

positions <- geozoo::simplex(p=4)$points

## To generate data
five_clusts <- gen_multicluster(n = c(450, 300, 150, 250, 350), p = 4, k = 5,
                       loc = positions,
                       scale = c(0.4, 0.35, 0.3, 1, 0.3),
                       shape = c("helicalspiral", "hemisphere", "unifcube", "bluntedcone", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)
```

>>>>

positions <- geozoo::simplex(p=4)$points
positions <- positions * 0.8

## To generate data
five_clusts <- gen_multicluster(n = c(2250, 1500, 750, 1250, 1750), p = 4, k = 5,
                       loc = positions,
                       scale = c(0.4, 0.35, 0.3, 1, 0.3),
                       shape = c("helicalspiral", "hemisphere", "unifcube", "bluntedcone", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)
```
